\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-23 intro.tex
heading changes based on Minh and discussion; also noted FP comments

We have developed, tested and deployed the Teleo-Reactive EXecutive
(\texttt{T-REX}) an on-board adaptive control system that integrates
AI based planning and %\sout{probabilistic} 
state estimation in a hybrid executive\cite{mcgann08a,mcgann08b,py10}. 
%  \sout{Probabilistic state estimation integrates a number of science observations to produce a
% likelihood that the vehicle sensors perceive a feature of
% interest}.\fcomment{\rx {\em does not} integrate probabilistic state
%   estimation! ... The HMM estimation was coded on top of \eu model but
%   neither \eu or \rx had explicit management of it} 
State estimation allow the system to keep track of the world evolution
as time advances based on a formal model distributed through the architecture.
Onboard planning and execution enables adaptation of
navigation and instrument control based on the state identified during
state estimation.
% \sout{the probability of having detected such a phenomenon} 
It further enables goal-directed
commanding within the context of projected mission state and allows
for replanning for off-nominal situations and opportunistic science
events. The framework in addition to being used on an AUV, is general
enough be used for controlling a personal robot \cite{mcgann2009} and
is deployed on a European planetary rover testbed
\cite{goac11}. While it is possible to integrate probabilistic
estimation on top of this framework \cite{mcgann08d}, such aspect is
out of scope of this chapter.
% Probabilistic state estimation through modeling within 
% this framework can be done is discussed elsewhere
% \cite{mcgann08d} and out of scope for this chapter. 
Deliberation and reaction are integrated systematically over different temporal and
functional scopes within a single agent and a single model that covers
the needs of high-level mission management, low-level navigation,
instrument control, and detection of unstructured and poorly
understood phenomena. \rx is deployed on MBARI's Dorado AUV shown in
Fig. \ref{fig:auv-fig}, which to the best of our knowledge is the only
operational marine platform anywhere being used for routine scientific
surveys with onboard plan synthesis.

>>>>

We have developed, tested and deployed the Teleo-Reactive EXecutive
(\rx) an on-board adaptive control system that integrates AI based
planning and state estimation in a hybrid
executive\cite{mcgann08a,mcgann08b,py10}.  State estimation allows the
system to keep track of world evolution as time advances based on a
formal model distributed through the architecture.  Onboard planning
and execution enables adaptation of navigation and instrument control
based on the state identified during state estimation.  It further
enables goal-directed commanding within the context of projected
mission state and allows for replanning for off-nominal situations and
opportunistic science events. The framework in addition to being used
on an AUV, is general enough be used for controlling a personal robot
\cite{pr2,Meeussen:2010dn,mcgann2009} and is deployed on a European
planetary rover testbed \cite{goac11}. While it is possible to
integrate probabilistic estimation on top of this framework
\cite{mcgann08d}, such representation is not explicitly handled by the
framework and is out of scope of this chapter.  Deliberation and
reaction are integrated systematically over different temporal and
functional scopes within a single agent and a single model that covers
the needs of high-level mission management, low-level navigation,
instrument control, and detection of unstructured and poorly
understood phenomena. \rx is deployed on MBARI's \emph{Dorado} AUV
shown in Fig. \ref{fig:auv-fig}, which to the best of our knowledge is
the only operational marine platform anywhere being used for routine
scientific surveys with onboard plan synthesis.
